---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r, echo=TRUE}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?
```{r, echo=TRUE}
totals <- aggregate(activity$steps, list(activity$date), sum)
names(totals) <- c("Date", "Steps")
hist(totals$Steps, 
     main = "Histogram of Total Steps Per Day",
     xlab = "Steps Per Day")
mean <- mean(totals$Steps, na.rm=TRUE)
median <- median(totals$Steps, na.rm=TRUE)
```
The mean is `r format(mean, nsmall=2)` steps per day.  
The median is `r median` steps per day.

## What is the average daily activity pattern?
```{r, echo=TRUE}
stepsByInterval <- aggregate(steps ~ interval, activity, "mean")
plot(stepsByInterval,
     main="Average Daily Activity in 5-minute Intervals",
     xlab="Interval",
     ylab="Average Step Count",
     type="l")
maxIndex <- which.max(stepsByInterval$steps)
```
The interval with the maximum number of steps is `r stepsByInterval$interval[maxIndex]`


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
